\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
% moderncv themes
\moderncvstyle{classic}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\usepackage[utf8]{inputenc}
\inputencoding{latin1}
\inputencoding{utf8}
\usepackage{hyperref}
\hypersetup{colorlinks,urlcolor=blue}
\usepackage[utf8]{inputenc}                    \usepackage[scale=0.75]{geometry}

% personal data
\name{Louie D.}{Corpe}
\title{Graduate Student in Particle Physics}
\address{14 Sidney Terrace}{CM23 3TU}{Bishops Stortford}
\phone[mobile]{+447948343026}                  
\email{ldcorpe@msn.com}                               % optional, remove / comment the line if not wanted
%\homepage{www.johndoe.com}                         
%\extrainfo{additional information}                 
%\photo[64pt][0.42pt]{picture}                       
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

\newcommand\myitem{ \vspace{0.15cm} \item \normalsize }
\newcommand\mybibforeword{}
\newcommand\mysection[1]{\section{#1}}

\renewcommand*{\cventry}[7][.25em]{%
 \vspace{0.15cm}
  \cvitem[#1]{#2}{%
    {\bfseries#3}%
    \ifthenelse{\equal{#4}{}}{}{, {\slshape#4}}% I changed this line (with comma) ...
      %\ifthenelse{\equal{#4}{}}{}{ {\slshape#4}}% ... into this one (without comma).
      %\ifthenelse{\equal{#5}{}}{}{, #5}%
      %\strut%
      \ifx&#5&%
      \else{\newline{}\begin{minipage}[t]{\linewidth}\normalsize#5\end{minipage}}\fi
      \ifthenelse{\equal{#6}{}}{}{\vspace{0.15cm} #6}%
      \strut%
      \ifx&#7&%
      \else{\newline{}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}}

\renewcommand*{\cvdoubleitem}[5][.25em]{%
 \cvitem[#1]{#2}{%
   \begin{minipage}[t]{\doubleitemmaincolumnwidth}#3\end{minipage}%
   \hfill% fill of \separatorcolumnwidth
   \begin{minipage}[t]{1.5\hintscolumnwidth}\raggedleft\hintstyle{#4}\end{minipage}%
   \hspace*{\separatorcolumnwidth}%
   \begin{minipage}[t]{\doubleitemmaincolumnwidth}#5\end{minipage}}}

\renewenvironment{thebibliography}[1]%
  {    
  \bibliographyhead{\refname}%
%    \small%
\mybibforeword
    \begin{list}{\bibliographyitemlabel}%
      {%
        \setlength{\topsep}{0pt}%
        \setlength{\labelwidth}{\hintscolumnwidth}%
        \setlength{\labelsep}{\separatorcolumnwidth}%
        \leftmargin\labelwidth%
        \advance\leftmargin\labelsep%
        \@openbib@code%
        \usecounter{enumiv}%
        \let\p@enumiv\@empty%
        \renewcommand\theenumiv{\@arabic\c@enumiv}}%
        \sloppy\clubpenalty4000\widowpenalty4000%
%        \sfcode`\.\@m%
%        \sfcode `\=1000\relax%
  }%
  {%
    \def\@noitemerr{\@latex@warning{Empty `thebibliography' environment}}%
    \end{list}%
  }


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\section{Experience}
\cventry{2013--present}{Imperial College (IC), CMS collaboration}{PhD Student}{London, CERN (Geneva)}{  % arguments 3 to 6 can be left empty
My PhD involved the study of the Higgs boson decaying into two photons ($H\rightarrow\gamma\gamma$) in data collected at the CMS experiment during proton-proton collisions in the second run of the Large Hadron Collider (LHC). One year of the PhD was spent on attachment at CERN in Switzerland. I am due to submit my thesis in April 2017.\vspace{-0.3cm}}{
\begin{itemize}%
%\setlength\itemsep{0.42em}
\myitem I was one of the main analysts preparing the CMS $H\rightarrow\gamma\gamma$ results using data collected during the second run of the LHC~\cite{PAS-HIG-15-005,PAS-HIG-16-020}. We produced a new observation of the Higgs boson, with over 5$\sigma$ significance. My responsibilities included:
\begin{itemize}
%\setlength\itemsep{0.25em}
\item modelling the signal and background in the main analysis.
\item performing the unblinding and statistical interpretation of the data.
\item co-editing the public physics analysis summary for our ICHEP 2016 result~\cite{PAS-HIG-16-020}.
\end{itemize}
%
%
\myitem I helped build and maintain a new software framework for use in diphoton decay analyses (\texttt{FLASHgg} and \texttt{FLASHggFinalFits}). My responsibilities included:
\begin{itemize}
%\item performing initial studies into jet reconstruction using the PUPPI algorithm. 
\item propagating systematic uncertainties into final result.
\item developing and maintaining the signal and background modelling tools.
\end{itemize}
%
%
\myitem I determined the photon identification efficiency of the proposed High Granularity Calorimeter (HGC) project for the CMS upgrade at the time of the High-Luminosity LHC (HL-LHC). The HGC was selected as the official upgrade choice, and my work was included in the technical proposal~\cite{CMSPhaseII}.
%
%
\myitem I was part of the 2015 CMS Electromagnetic Calorimeter (ECAL) calibration team. I was responsible for validating calibrations and monitoring of the stability of the measured Z-boson mass, with the first data of the second LHC run.
%
%
\myitem I assessed the photon energy resolution in the CMS ECAL during the first run of the LHC, using simulated $H\rightarrow\gamma\gamma$ photons. My work was included in the reference paper for CMS photon reconstruction performance in the first run~\cite{PhotonPerformance}.
%
%
\myitem I was responsible for projecting the 2016 $H\rightarrow\gamma\gamma$ results to the conditions of the HL-LHC for the ECFA 2016 workshop~\cite{CMS-DP-2016-064}. This extrapolation was used to inform discussion on future physics strategy.
%
%
\myitem I represented the $H\rightarrow\gamma\gamma$ analysis team in the CMS Higgs Combinations Group. I was responsible for validating the inputs to the CMS statistical interpretation tools for all analyses involving Higgs decays to photons.
%
%
\myitem I performed data-taking shifts at CMS in the role of Detector Control System shifter, monitoring the status of sub-detectors and checking for safety issues.
\end{itemize}
}
%
%
%
\cventry{2011--2013}{Adobe Systems (Formerly Efficient Frontier)}{Associate Account Manager}{London}{
Efficient Frontier was a startup selling automated advertising technology for pay-per-click adverts on search engines. I worked as part of a team managing large online advertising campaigns for a range of clients of different sizes. Efficient Frontier was acquired by Adobe in early 2012 as part of their media optimization offering.
}{}
%
%
%
\cventry{2010--2011}{University College London (UCL)}{MSci Project}{London}{  % arguments 3 to 6 can be left empty
My MSci project, \emph{Helicity -- from Clifford to Graphene}, was supervised by Christian Gerhard Boehmer (UCL). We determined the mathematical link between disjoint definitions of helicity (as a Clifford algebra in mathematics, and as a bilinear covariant in theoretical physics). We found an unexpected application relevant to the propagation of electrons in superconducting graphene.
Our findings were published in Journal of Physics A: Mathematical and Theoretical.~\cite{MastersProject}
}{}
%
%
%
\section{Education}
\cventry{2007--2011}{MSci Mathematics and Physics}{University College London}{First Class Honours}{}{}  % arguments 3 to 6 can be left empty
\cventry{2003--2007}{French Baccalaureate, Section Scientifique}{Lycée Condorcet, Sydney, Australia}{Mention Très Bien, Félicitations du Jury}{}{}
%
%
%
\section{Teaching Experience}
\cventry{2016}{Undergraduate Summer Projects}{Imperial College}{Project supervisor for four students}{}{}
\cventry{2016}{Undergraduate Advanced Particle Physics}{Imperial College}{Coursework marker and demonstrator for 4th year students}{}{}
\cventry{2015, 2016}{Undergraduates Labs}{Imperial College}{1st Year Lab demonstrator: electromagnetism and optics}{}{}
\cventry{2015, 2016}{CEA@Islington Project}{UCL and Ambler Primary School}{Mathematics teaching assistant}{}{}
%
%
%
\section{Outreach Experience}
\cventry{2016}{Particle Physics Masterclass}{Imperial College}{Demonstrator for secondary school students}{}{}
\cventry{2015}{Royal Society Summer Exhibition}{Royal Society, London}{Exhibit designer and shifter}{}{}
\cventry{2011}{Mathematics Department Podcast}{UCL}{Podcast co-writer, researcher and co-host}{}{}%
%
%
%
\section{Talks}
\cventry{2016}{Higgs Couplings 2016}{SLAC, California, USA}{Higgs to gamma gamma decays: inclusive and differential results}{}{}
\cventry{2016}{Higgs Hunting 2016 (Young Scientists Forum)}{UPMC, Paris, France}{Search for the Standard Model Higgs Boson decaying to two photons in Run II LHC collisions at CMS}{}{}
\cventry{2016}{HIG-16-020 Approval}{CERN, Geneva, Switzerland}{Updated measurements of Higgs boson production in the diphoton decay channel at centre-of-mass energy 13~TeV}{}{}
\cventry{2016}{IOP HEP \& APP joint conference}{University of Sussex, Brighton, UK}{Searching for the Higgs Boson decaying to photons in Run II LHC collisions at CMS}{}{}
\cventry{2015}{ECAL days}{University of Trieste, Trieste, Italy}{Clustering and Pileup mitigation}{}{}
%
%
%
\section{Computing skills}
\cvdoubleitem{Typesetting}{\LaTeX}{Coding Languages}{\texttt{C$++$, Python, bash }}{}
\cvdoubleitem{Data Analysis}{\texttt{Root, RooFit}}{Machine Learning }{\texttt{TMVA}}{}
%
%
%
\vspace{0.42cm}
\section{Languages}
\cventry{French}{Fluent}{Raised in France, educated in French}{}{}{}
\cventry{German}{Conversational}{Studied for 6 years during education.}{}{}{}

\vspace{0.42cm}
\section{Academic Awards}
\cventry{2011}{UCL Castillejo Prize For Mathematics and Physics} {}{Winner}{}{}
\cventry{2007}{French Baccalaureate}{}{Congratulations from the examination board \emph{(Félicitations du Jury)}}{}{}
\cventry{2006}{Australian Science Olympiads National Qualifying Exam}{}{High Distinction}{}{}

\vspace{0.42cm}
\section{Memberships and Collaborations}
\cventry{2016--present}{Institute of Physics}{Associate Member}{}{}{}
\cventry{2014--present}{CMS Collaboration}{Member}{}{}{}


\vspace{0.42cm}
% Publications from a BibTeX file without multibib
%  for numerical labels: 
\renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): 
  \renewcommand{\refname}{Publications}{}
\renewcommand{\mybibforeword}{ I am a co-author on 152 citeable papers as part of the CMS collaboration (inSPIRE HEP, November 2016), with a h$_\textrm{HEP}$ index of 28. Papers to which I have made a substantial contribution are listed below. \vspace{0.3cm}}
  \nocite{*}
  \bibliographystyle{lucas_unsrt}
  \bibliography{publications}                        % 'publications' is the name of a BibTeX file

  \section{References}
\cventry{(Supervisor)}{Professor Paul Dauncey}{Professor of Particle Physics (Imperial College)}{p.dauncey@imperial.ac.uk}{}{}
\cventry{}{Professor Sir Tejinder Virdee FRS}{Professor of Physics (Imperial College)}{tejinder.virdee@cern.ch}{}{}
\cventry{}{Doctor Andr\'e Tinoco Mendes David}{Research Physicist (CERN)}{andre.david@cern.ch}{}{}

  \clearpage
  \end{document}
